Examining Whether Approximate Visualizations Impact Perception of Corrected Visualizations

### 2016-12-11 paper/paper.tex
No color links

\usepackage[pdftex, colorlinks]{hyperref}
\newcommand{\figref}[1]{\hyperref[#1]{Figure~\ref*{#1}}}
\newcommand{\secref}[1]{\hyperref[#1]{Section~\ref*{#1}}}
\newcommand{\tabref}[1]{\hyperref[#1]{Table~\ref*{#1}}}
\newcommand{\ea}{{et~al.}\xspace}

@@

The regression tables of our three types of questions are in tables \ref{table_q1}, \ref{table_q2}, and \ref{table_q3}.
The raw data for our three types of questions are in figures \ref{figure_q1}, \ref{figure_q2}, and \ref{figure_q3}.
We now answer our research questions in turn.

@@

We used linear regression in all of our statistical analyses.
We made this choice because our outcome is numeric rather than categorical.
Additionally, we had no reason to anticipate our data would fit a different distribution.
However, viewing figures \ref{figure_q1}, \ref{figure_q2}, and \ref{figure_q3} shows that although much of the data appears distributed around 0 measured bias, there are many participant responses far away from this value.
These responses do not appear to necessarily be outliers, meaning that many people were answering questions similarly wrong.

>>>>

\usepackage[pdftex]{hyperref}
\newcommand{\figref}[1]{\hyperref[#1]{Figure~\ref*{#1}}}
\newcommand{\secref}[1]{\hyperref[#1]{Section~\ref*{#1}}}
\newcommand{\tabref}[1]{\hyperref[#1]{Table~\ref*{#1}}}
\newcommand{\ea}{{et~al.}\xspace}

@@

The regression tables of our three types of questions are in Tables~\ref{table_q1}, \ref{table_q2}, and \ref{table_q3}.
The raw data for our three types of questions are in Figures~\ref{figure_q1}, \ref{figure_q2}, and \ref{figure_q3}.
We now answer our research questions in turn.

@@

We used linear regression in all of our statistical analyses.
We made this choice because our outcome is numeric rather than categorical.
Additionally, we had no reason to anticipate our data would fit a different distribution.
However, viewing Figures~\ref{figure_q1}, \ref{figure_q2}, and \ref{figure_q3} shows that although much of the data appears distributed around 0 measured bias, there are many participant responses far away from this value.
These responses do not appear to necessarily be outliers, meaning that many people were answering questions similarly wrong.
